

\section{Accommodation}

A&O, the hostel situated next to the train station (and hence about 35 minutes by foot from the venue) costs about 10 for shared accommodation. Private dorms are also available for the cost of 25 euros. 

As we would like to keep everyone located in the same area, we would like to host keynote speakers rooms at the hotel Ibis located just on the other side of the train station. 
Alternatively, B&B, another hostel, is offering rooms for about 25 euros per person sharing if need be. 


\section{Dining}

\section{Breakfast}
There are little German bakeries all over the city where you can get breakfast (savory or sweet pastries and coffee or tea) for about 4 euros. However, breakfast is included in room fares at the Ibis hotel and A&O, as well B&B have common dining rooms and kitchen where everyone can prepare their usual breakfast.
 
\subsection{Lunch}
The university canteen offers meals for about 3 euros. Otherwise, all type of restautrants (kebabs, thai,chinese, italian etc.) are available all over the inner city. On average, one should budget about 6 euros per meal.


\subsection{Dinner}
We intend to organize a picnic in the “Schlosspark” on Tuesday, as well as a BBQ on Friday. For the other evenings, we would suggest to have dinner at one of the three “Hammer” options (Kippe, Emaille, Blue) for under a fiver, including a glass of beer! Of course, other options are available in this city which is known for its student-friendly prices!


As you can see, accessibility of the location, prices of accommodation and meals, as well as the overall concept elaborated by the organizing committee are all speaking in favor of hosting GUADEC in August 2016 in the sunny city of Karlsruhe! We are looking forward to welcoming you!

\section{Budget}
\section{Bibliograpyh and credits}